---
output: github_document
---
<!-- Readme document of LandComp R package -->
<!-- badges: start -->
[![R-CMD-check](https://github.com/ladylavender/LandComp/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ladylavender/LandComp/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  #out.width = "100%",
  fig.width = 10, fig.height = 5
)
```

# LandComp

'LandComp' is a package for quantifying landscape diversity and structure at
multiple scales. For these purposes Juhász-Nagy's functions, i.e. compositional 
diversity (CD) and associatum (AS), are calculated.

## Installation

You can install the development version of LandComp using the following command:

``` r
install.packages("devtools")
devtools::install_github("ladylavender/LandComp")
```

## Example

Example regular grids represent demonstrative spatial arrangements. They reflect a typical case when having presence/absence data on some landscape classes (e.g. vegetation types here) along a landscape. 
Note, there are three requirements of using the `LandComp` package:

* the landscape data should be numeric binary, i.e. it should contain 0 or 1 values
* the geometry of the landscape data should be a regular square or hexagonal grid
* the geometry of the landscape data should have projected coordinates (i.e. WGS84 is not eligible)

### Regular square grid data

The structure and the visualization of the example square grid data:

```{r square_data, echo = TRUE}
suppressPackageStartupMessages(library("sf"))
library(LandComp)
data("square_data")
plot(square_data)
str(square_data)
```

Two values of CD and AS measuring landscape diversity and structure can be calculated as e.g.

```{r square_example, echo=TRUE}
LandComp(x = square_data, aggregation_steps = 0:1)
```

### Regular hexagonal grid data

The structure and the visualization of the example hexagonal grid data:

```{r hexagonal_data, echo = TRUE}
data("hexagonal_data")
plot(hexagonal_data)
str(hexagonal_data)
```

```{r hexagonal_example, echo=TRUE}
LandComp(x = hexagonal_data, aggregation_steps = 0:1)
```

For further information and examples, see both the vignette of the package and `?LandComp` after installing the package.  
Note, if you would like to view the vignette from R using the code `vignette("LandComp")`, you should install the package using the following command:

``` r
devtools::install_github("ladylavender/LandComp", build_vignettes = TRUE)
```
