---
output: github_document
---
<!-- Readme document of LandComp R package -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  #out.width = "100%",
  fig.width = 10, fig.height = 5
)
```

# LandComp

LandComp is a package for quantifying landscape diversity and structure at
multiple scales. Juh`r "\U00E1"`sz-Nagy's functions, i.e. compositional diversity and
associatum are used for these purposes.

## Installation

You can install the development version of LandComp using the following command:

``` r
install.packages("devtools")
devtools::install_github("ladylavender/LandComp")
```

## Example

Suggest we have data on some vegetation types along a landscape. Note, there are three requirements:

* the landscape data should be numeric binary, i.e. it should contain 0 or 1 values
* the geometry of the landscape data should be a regular square or hexagonal grid
* the geometry of the landscape data should have projected coordinates (i.e. WGS84 is useless)

### Example for using regular square grid

Let's have a look at the square grid data.

```{r square_data, echo = TRUE}
suppressPackageStartupMessages(library("sf"))
library(LandComp)
data("square_data")
plot(square_data)
str(square_data)
```

Two values of CD and AS measuring landscape diversity and structure can be calculated as e.g.

```{r square_example, echo=TRUE}
LandComp(x = square_data, aggregation_steps = 0:1)
```

### Example for using regular hexagonal grid

Let's have a look at the hexagonal grid data.

```{r hexagonal_data, echo = TRUE}
data("hexagonal_data")
plot(hexagonal_data)
str(hexagonal_data)
```

```{r hexagonal_example, echo=TRUE}
LandComp(x = hexagonal_data, aggregation_steps = 0:1)
```
